---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarystats

<!-- badges: start -->
<!-- badges: end -->

The goal of `summarystats` is to provide a simple and efficient way to calculate summary statistics for a numerical variable grouped by a categorical variable. This package is useful for data exploration and quick analysis of summary metrics such as minimum, maximum, mean, median, standard deviation, and count within each category.

## Installation

You can install the development version of `summarystats` from GitHub with:

```r
# Install summarystats package from GitHub
devtools::install_github("stat545ubc-2024/summarystats", ref="0.2.0")
```

## Example

This is a basic example that shows how to use the `summary_stats_variable` function to calculate summary statistics for a numerical variable grouped by a categorical variable:

```{r example}
library(summarystats)

# Calculate summary statistics for the variable 'Sepal.Length' grouped by 'Species' from the iris dataset
summary_stats_variable(iris,Species,Sepal.Length, na_handling=TRUE)
